---
title: "Data Science"
format: html
editor: visual
---

### What is being a data scientist about?

A data scientist is about transforming raw data into meaning. A data scientist cleans raw data and gathers insights through analysis . Data scientists discover patterns in data through modeling and inference. A data scientist's goal can be to summarize and explore a data set, compare different groups, find an optimal business solution, use regression to project a numerical value, predict the classification of a new observation, and so much more! A data scientist must also be skilled in communicating their findings.

### Data Scientists vs Statisticians - Differences/Similarities

Data scientists and statisticians both gather meaningful insights from data to help organizations solve problems, but their focuses are slightly different.

**Statistician**

-   Mainly focuses on modeling
-   Data is relatively small in size and clean in text file formats.
-   Work with mostly structured data
-   Bring data to models

**Data Scientist**

-   Mainly focuses on business problem and result
-   Work with messy and large amounts of data in various formats
-   Work with structured and unstructured data
-   Bring models to data

### How do I view myself in relation to these two areas?

I don't currently view myself as either of these, but I am most interested in becoming a data scientist. So far in my graduate classes, I have enjoyed learning programming languages and learning all the ways to clean and explore data sets. I also think those two areas overlap. I still need to have a solid foundation in statistical analysis to be a successful data scientist.

### Iris Dataset

Create object y.
```{r}
y <- density(iris$Petal.Width)
```

Determine the class, type, and structure of object y.
```{r}
class(y)
typeof(y)
str(y)
```

Use the plot function on y and hide the R code. 
```{r}
#| echo: false 
plot(y)
```

